Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\section{Introduction and related work}
We are witnessing a constant increase of the rate at which data is being produced and made available in machine readable formats. Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e. not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering non independent and identically distributed (non i.i.d.) data. This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis. As cursory examples of application domains that are particularly  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship or co-authorship, bioinformatics, where nodes are proteins and metabolites and edges represent a type of chemical interaction such as catalysis or signaling, and e-commerce, where nodes are people and goods and edges encode a ''buy'' or ''like'' relationship.

However, despite the availability of huge data, most graphs are only partially observed graphs. That means a number of actual links in each graph are absent or missing. Tackling this issue is a necessary condition to obtain high performance graph-based predictive systems. As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links. A graph could be associated with external information sources, so called "side information". Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes. An expected method is required to make use of both such kind of data sources. In this paper, we only focus on the topological information. Thus we the term link prediction methods to refer to topology-based link prediction methods. Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.

>>>>

\section{Introduction and related work}
We are witnessing a constant increase of the rate at which data is being produced and made available in machine readable formats. Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e. not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering non independent and identically distributed (non i.i.d.) data. This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis. As cursory examples of application domains that are particularly  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship or co-authorship, bioinformatics, where nodes are proteins and metabolites and edges represent a type of chemical interaction such as catalysis or signaling, and e-commerce, where nodes are people and goods and edges encode a ''buy'' or ''like'' relationship.
A key characteristic of this type of data collections is the sparseness and dynamic nature, i.e. the fact that the number of recorded relations is significantly smaller than the number of all possible pairwise relations, and the fact that these relations evolve in time. A crucial computational task is then the ''link prediction problem'' which allows to suggest friends, or possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease, or to suggest novel products to be bought to a customer.

As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links. A graph could be associated with external information sources, so called "side information". Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes. An expected method is required to make use of both such kind of data sources. In this paper, we only focus on the topological information. Thus we the term link prediction methods to refer to topology-based link prediction methods. Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.
